---
title: "Time Series Forecasting Shiny App"
author: "Matiki"
date: "November 19, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forecast)
library(dplyr)
```

## Time Series of US Accidental Deaths 1973-1978

This Shiny app uses the sample data set 'USAccDeaths' which is a monthly time 
series of the total accidental deaths in the US from 1973 to 1978. We will be 
using this time series to do some forecasting using various types of forecasting
models. Using the 'forecast' package, developed by Rob Hyndman, we will create 
the models as well as plot the forecast periods along with 80% and 95% confidence
intervals.

In order to compare the accuracy of the different models, we will need to first
split the time series into training and test sets. This will allow us to compare
the accuracy of each model by looking at the root mean squared error (RMSE).

## Types of Forecast Models

Here are the types of models that we will implement in our Shiny app:

- Naive model
- Seasonal naive model
- ARIMA model
- ETS Model
- Harmonic regression model
- TBATS model
- Exponential smoothing 
- Exponential smoothing with damped trend
- Exponential smoothing with additive seasonality
- Exponential smoothing with multiplicative seasonality

## Exmple what the app will display:
```{r}
training <- window(USAccDeaths, end = 1977)
test <- window(USAccDeaths, start = 1977)
training %>% auto.arima() %>% forecast() %>% autoplot() + autolayer(test)
```

## Input from User

The user will be able to select which type of forecast to implement, how many 
months make up the forecast period, and the number of fourier terms to 
include in a harmonic regression model, if they should choose to use this model
in their forecast.

There will also be a second tab on the app displaying the accuracy like this:
```{r}
training %>% auto.arima() %>% forecast() %>% accuracy(test)
```